# rdatabricks

An R Package that wraps the Databricks REST API. You can find the API at
https://docs.databricks.com/api/index.html. This package is designed assuming
you're a paying customer of DataBricks.

The idea is to implement the cluster admin API (using their v2.0 API) and the command execution API (v1.2)

This package also contains engine for knitr so you can run RMarkdown documents
with codeblocks that call code that will be run on remote clusters.


## Examples of context creation and command execution

Set configuration parameters

```{r}
options(databricks = list(
            instance  = "instance",
            clusterId = 'ciid',
            user      = "user",
            password  =  "pwd"))
```


create a context (parameters are taken from `options`), default language is python.

```{r}
ctx <- dbxCtxMake()
ctxStats <- dbxCtxStatus(ctx)
isContextRunning(ctxStats)
```

Send a command to the context (default language is python)

```{r}
cmd <- '
import sys
import datetime
import random
import subprocess

from pyspark.sql import SparkSession
spark = SparkSession.builder.getOrCreate()
ms = spark.read.option("mergeSchema", "true").parquet("s3://telemetry-parquet/main_summary/v4/")
ms.createOrReplaceTempView("ms")
'

cid <- dbxRunCommand(cmd,ctx=ctx)
while(TRUE){
    r <- dbxCmdStatus(cid,ctx)
    if(!isCommandRunning(r)) {cat("\n"); break}
    cat("." )
    Sys.sleep(5)
    ## this loop is equivalent to dbxRunCommand(cmd,ctx=ctx,wait=5)
}
$id
[1] "e90e0e8688ad45408d5733611d04a218"

$status
[1] "Finished"

$results
$results$resultType
[1] "text"

$results$data
[1] ""
```


See an error

```{r}
cid3 <- dbxRunCommand("x+o",ctx=ctx,wait=5)
Waiting for command: 85475c026fb44ffdb44bf3d72a9c6716 to finish
$id
[1] "85475c026fb44ffdb44bf3d72a9c6716"

$status
[1] "Finished"

$results
$results$resultType
[1] "error"

$results$summary
[1] "<span class=\"ansired\">NameError</span>: name &apos;x&apos; is not defined"

$results$cause
[1] "---------------------------------------------------------------------------\nNameError                                 Traceback (most recent call last)\n<command--1> in <module>()\n----> 1 x+o\n\nNameError: name 'x' is not defined"
```



Get plot output

```{r}

cmd2 <- '
import numpy as np
import matplotlib.pyplot as plt
x = np.linspace(0, 2*np.pi, 50)
y = np.sin(x)
y2 = y + 0.1 * np.random.normal(size=x.shape)
fig, ax = plt.subplots()
ax.plot(x, y, "k--")
ax.plot(x, y2, "ro")
ax.set_xlim((0, 2*np.pi))
ax.set_xticks([0, np.pi, 2*np.pi])
ax.set_ylim((-1.5, 1.5))
ax.set_yticks([-1, 0, 1])
ax.spines["left"].set_bounds(-1, 1)
ax.spines["right"].set_visible(False)
ax.spines["top"].set_visible(False)
ax.yaxis.set_ticks_position("left")
ax.xaxis.set_ticks_position("bottom")
display(fig)
'

cid2 <- dbxRunCommand(cmd2,ctx=ctx,wait=2)
Waiting for command: 70559981ebb6420eadfb3ea33adf2603 to finish
$id
[1] "70559981ebb6420eadfb3ea33adf2603"

$status
[1] "Running"

$results
NULL

$id
[1] "70559981ebb6420eadfb3ea33adf2603"

$status
[1] "Finished"

$results
$results$resultType
[1] "image"

$results$fileName
[1] "/plots/78fa8d5e-47c3-4622-aad1-7c83d1c6cf4e.png"
```

## todo

- complete the cluster admin API
- library install API
- jobs API


